# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data

Read and present the data
```{r}

t=read.csv("activity.csv")
head(t)
summary(t)
# Interval value vs index
plot(seq(1,dim(t)[1]),t$interval,xlab="Row number",ylab="interval")

```
It is a saw teeth function  
<br><br>

The first day there is no data , so we take it out. Then we show how the steps are distributed by day (four days are presented)
```{r}
ts=t[-seq(1,288),]
#ts_day=ts[seq(1,which(ts$interval==max(ts$interval))[1]),]
par(mfrow=c(2,2)) 
ts_day=ts[ts$date=="2012-10-02",]
plot(ts_day$interval,ts_day$steps,type = "l",xlab="interval",ylab="steps")
ts_day=ts[ts$date=="2012-10-03",]
plot(ts_day$interval,ts_day$steps,type = "l",xlab="interval",ylab="steps")
ts_day=ts[ts$date=="2012-10-04",]
plot(ts_day$interval,ts_day$steps,type = "l",xlab="interval",ylab="steps")
ts_day=ts[ts$date=="2012-10-05",]
plot(ts_day$interval,ts_day$steps,type = "l",xlab="interval",ylab="steps")
```



## What is mean total number of steps taken per day?
```{r}
totalStepsPerDay=tapply(t$steps,t$date,function(x) sum(x,na.rm = TRUE))
par(mfrow=c(1,2)) 
plot(totalStepsPerDay)
hist(totalStepsPerDay)
par(mfrow=c(1,1)) 
#mean
mean(totalStepsPerDay)
#median
median(totalStepsPerDay)
```


## What is the average daily activity pattern?

#### Time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r}
meanStepsPer5Min=tapply(t$steps,t$interval,function(x) mean(x,na.rm = TRUE))
plot(meanStepsPer5Min,xlab="5 min interval", ylab="mean steps", type="l")
```


#### Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
names(which(meanStepsPer5Min==max(meanStepsPer5Min)))

```




## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
